%% start of file `coverletter.tex'.
% !TEX root = presentation/coverletter_only.tex

%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK

% recipient data
\recipient{Layne Cairo, Senior Technical Recruiter}
{Bluebeam
	\\Pasadena, CA}

\date{August 30, 2024}
\opening{\\Dear Ms. Cairo,}
\closing{Sincerely,}
%\enclosure[Attached]{curriculum vit\ae{}}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname
\makelettertitle


I was excited come across Bluebeam while looking around LinkedIn, and I'd like to apply to your Staff Software Engineer position.
The construction industry makes up \textcolor{color1}{\href{https://fred.stlouisfed.org/series/VAPGDPC}{over 4\% of US GDP}},
and is unlikely to go anywhere even with how chaotic our world is becoming.
I have nearly 10 years of SaaS experience with a variety of companies and teams, 
and I'd love the opportunity to leverage that in an industry that's more concrete.

In my last position at Spotify, I was the Tech Lead for a large team tasked with evaluating and implementing new product ideas
and partner integrations in support of the Ads Business Development department.
I helped build that team from the ground up after being connected with someone on the business side to develop a proof-of-concept
for an ad product UX hypothesis at the start of 2020. My work with that was successful enough that leadership provided us with resources
to scale the product (now called The Stage) into a multi-service system, and we began hiring in 2021.
I played a major role in interviewing candidates and making hiring decisions,
and led much of the work in planning and developing our team culture.
In 2022, my team's continued success in growing The Stage led us to be assigned even more resources,
as well as an expanded remit to work on on other high-value projects that the main Ads organization couldn't or wouldn't prioritize.
My team's work brought in more than \$70 million of added revenue in 2023, by which time we had grown to 22 people.

Throughout my career, I've always valued the opportunity to learn things when a project demands it.
I picked up mobile development to build the first version of The Stage, leaned into system design when we needed to scale it,
and practiced mentorship, process design, and culture planning (all remotely) when we needed to build a team around it.
I  hold high standards for myself when it comes to the work I do, and I'm good at soliciting and responding to
feedback to ensure that the quality of my deliverables never drops. In leadership roles, I endeavor to
convey that focus on quality in my delegation and feedback to my teammates to ensure the best possible outcomes
with the greatest possible scope.
I'm confident that I'll be able to bring this flexibility and focus on quality to bear to solve whatever problems
you need your team to tackle.

I look forward to meeting you and the team, and to learning how I might be able to support Bluebeam.
Thank you for your time and consideration.


\vspace{10pt}

\makeletterclosing

%\clearpage\end{CJK*} % if you are typesetting your resume in Chinese using CJK; the \clearpage is required for fancyhdr to work correctly with CJK, though it kills the page numbering by making \lastpage undefined

%% end of file `coverletter.tex'.
