%% start of file `resume.tex'.

\input{config.tex}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\makecvtitle


\section{Experience}
\cventry{2021-2023}{Spotify USA Inc.}{Senior Engineer}{Oakland, CA}
	{Tech Lead position}{
	\begin{itemize}
	\item Defined the technical strategy for a product area of 22 (13 engineers), incl. system design and mentoring
	\item Continued development of the WebView feature from a proof-of-concept to a production feature which powered \textcolor{color1}{\href{https://newsroom.spotify.com/2023-10-18/spotifys-interactive-experiences-create-the-magic-of-wrapped-year-round/}{many high-profile campaigns}}, including 2023 Wrapped, and brought in >\$50MM in 2023
	\item Led a company priority project (incl. 8 cross-functional teams) to place video ads on smart TVs (eg. Roku)
	\end{itemize}
	}
\cventry{2020-2021}{Spotify USA Inc.}{Engineer II}{Oakland, CA}
	{Full-stack experimentation position (Java/Android/iOS/Typescript)}{
	\begin{itemize}
	\item Developed a custom WebView feature in the Spotify Music app (Android and iOS) to test a UX hypothesis
	\item Ran a public-facing alpha test targeting 50\% of Canadian users and demonstrated 178\% increased engagement
	\item Mentored a junior coworker in frontend (React.js) and backend (Java) web development
	\end{itemize}
	}
\cventry{2019}{Spotify USA Inc.}{Engineer II}{Oakland, CA}
	{Backend web development position (Java/SQL)}{
	\begin{itemize}
	\item Acted as the technical owner and principal architect on a team which developed a service that placed ads targeted using first-party listening data on third-party platforms
	\item Worked directly with contacts at Facebook to ensure compatibility with their ad network
	\end{itemize}
}

\cventry{2016-2018}{Spotify USA Inc.}{Engineer I}{San Francisco, CA}
	{Full-stack web development position (React.js/Java)}{}
\cventry{2016}{Preact, Inc}{Software Engineer}{San Francisco, CA}
	{Lead frontend web development position (React.js)}{}
\cventry{2014-2015}{Revinate, Inc}{Software Engineer}{San Francisco, CA}
	{Full-stack web development position (PHP)}{}
\cventry{2012-2014}{Google Inc.}{Internal Technology Resident}{Mountain View, CA}	
	{Fixed-Term Residency supporting and improving Google's infrastructure}{}
%\cventry{year--year}{Job title}{Employer}{City}{}{Description line 1\newline{}Description line 2}
%\subsection{Miscellaneous}

\section{Education}
\cventry{2008-2012}{Johns Hopkins University}{Bachelor of Science}{Baltimore, MD}{\textit{GPA: 3.64}}{Biomedical Engineering with Instrumentation (Electrical Engineering) focus}  % arguments 3 to 6 can be left empty

\section{Skills}
\begin{cvcolumns}
  \cvcolumn{Languages}{
  \begin{itemize}
	\item Java
	\item SQL
	\item Typescript
	\item Kotlin/Swift
  \end{itemize}
  }
 \cvcolumn{Frameworks}{
 \begin{itemize}
	\item Spotify Apollo
	\item React.js
	\item Android
	\item iOS
 \end{itemize}
 }
  \cvcolumn{DevOps}{
  \begin{itemize}
  	\item Linux
	\item PostgreSQL
  	\item Docker/Kubernetes
  	\item Google Cloud Platform
  \end{itemize}
  }
%  \cvcolumn{Hardware}{
%  \begin{itemize}
%  	\item Circuit Design
%  	\item  PCB Layout Design
%  \end{itemize}
%  }
\end{cvcolumns}


%\clearpage\end{CJK*} % if you are typesetting your resume in Chinese using CJK; the \clearpage is required for fancyhdr to work correctly with CJK, though it kills the page numbering by making \lastpage undefined
\end{document}


%% end of file `resume.tex'.
